Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-03-27 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Minor Corrections + Update pdf

HS acknowleges Catherine Etchebest and St\'ephane T\'eletch\'ea for useful discussions and continued support, GENCI-CINES for the HPC resources (Grant 2014-c2014077209).

>>>>

HS acknowleges Catherine Etchebest and St\'ephane T\'eletch\'ea for useful discussions and continued support, the HPC resources granted from GENCI-CINES (Grant 2014-c2014077209) and computer facilities provided by R\'egion Ile de France and INTS (SESAME 2009 project).
